### 2019-04-24 quali/tex/appendix/ellipse_intersection.tex
Refactoring

\begin{align*}
    b^2x^2 + a^2y^2 = b^2(x-h)^2 + a^2(y-k)^2 \\
    b^2(-2xh + h^2) + a^2(-2yk + k^2) = 0\\
    x(2hb^2) = b^2h^2 + a^2(-2yk + k^2)\\
    x = y\frac{-2yka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

@@

\begin{align*}
    \alpha = \frac{-2yka^2}{2hb^2} \\
    \beta = \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

>>>>

\begin{align*}
    b^2x^2 + a^2y^2 = b^2(x-h)^2 + a^2(y-k)^2 \\
    b^2(-2xh + h^2) + a^2(-2yk + k^2) = 0\\
    x(2hb^2) = b^2h^2 + a^2(-2yk + k^2)\\
    x = y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

@@

\begin{align*}
    \alpha = \frac{-2ka^2}{2hb^2} \\
    \beta = \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

### 2019-04-24 quali/tex/chapter/definicoes.tex
Refactoring

\section{Elliptical and euclidean norm functions}

@@

Let $u \in \R^2$ be a vector, the euclidean norm of $u$ is defined as

@@

\noindent the elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter. This matrix can be seen as a linear transformation of the euclidean norm. Let $u \in \R^2$ be a vector, the elliptical norm of $u$ is defined as

@@

It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the euclidean norm.

@@

A circle (or circumference) is a set of points in $\R^2$ that have constant euclidean distance, also known as radius, to another point, also referred to as the center of the circle. A unit circle is a circle with radius equal to $1$.

A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.

\begin{equation}\label{eq:disk}
||p-c||_2^2 \le 1
\end{equation}

@@

An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin its construction with two points called foci and a constant $R \in \R$, with $R$ being greater than the euclidean distance between the two foci points (see \autoref{fig:ellipse_with_foci}). The ellipse is, then, defined as the set of points whose distance to the foci is equal to $R$. In other words, let $f_1, f_2 \in \R^2$ be the two foci points, the ellipse is the set of every point $p \in \R^2$, such that $||p-f_1||_2 + ||p-f_2||_2 = R$. It can be shown that this definition is equivalent to \autoref{def:ellipse}, with the coverage of a point $p$ being equivalent to $||p-f_1||_2 + ||p-f_2||_2 \le R$.

@@

An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}. This can be understood as a scaling transformation applied to the euclidean norm.

@@

    \caption{The ellipse as a parametric curve}
    \input{tex/figures/ellipse_definition.tex}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

>>>>

\section{Elliptical and Euclidean norm functions}

@@

Let $u \in \R^2$ be a vector, the Euclidean norm of $u$ is defined as

@@

\noindent the elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter. This matrix can be seen as a linear transformation of the Euclidean norm. Let $u \in \R^2$ be a vector, the elliptical norm of $u$ is defined as

@@

It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.

@@

A circle (or circumference) is a set of points in $\R^2$ that have constant Euclidean distance, also known as radius, to another point, also referred to as the center of the circle. A unit circle is a circle with radius equal to $1$.

A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy

\begin{equation}\label{eq:disk}
||p-c||_2^2 \le 1.
\end{equation}

@@

An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin its construction with two points called foci and a constant $R \in \R$, with $R$ being greater than the Euclidean distance between the two foci points (see \autoref{fig:ellipse_with_foci}). The ellipse is, then, defined as the set of points whose distance to the foci is equal to $R$. In other words, let $f_1, f_2 \in \R^2$ be the two foci points, the ellipse is the set of every point $p \in \R^2$, such that $||p-f_1||_2 + ||p-f_2||_2 = R$. It can be shown that this definition is equivalent to \autoref{def:ellipse}, with the coverage of a point $p$ being equivalent to $||p-f_1||_2 + ||p-f_2||_2 \le R$.

@@

An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}. This can be understood as a scaling transformation applied to the Euclidean norm.

@@

    \caption{The ellipse as a parametric curve.}
    \input{tex/figures/ellipse_definition.tex}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

### 2019-04-24 quali/tex/figures/ellipse_gamma.tex
Refactoring

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,193); %set diagram left start at 0, and has height of 193

%Shape: Ellipse [id:dp10634347053631776] 
\draw   (68.5,97.75) .. controls (68.5,67.24) and (115.62,42.5) .. (173.75,42.5) .. controls (231.88,42.5) and (279,67.24) .. (279,97.75) .. controls (279,128.26) and (231.88,153) .. (173.75,153) .. controls (115.62,153) and (68.5,128.26) .. (68.5,97.75) -- cycle ;
%Shape: Ellipse [id:dp7816950476685691] 
\draw  [color={rgb, 255:red, 163; green, 163; blue, 163 }  ,draw opacity=1 ] (167.5,103.75) .. controls (167.5,73.24) and (214.62,48.5) .. (272.75,48.5) .. controls (330.88,48.5) and (378,73.24) .. (378,103.75) .. controls (378,134.26) and (330.88,159) .. (272.75,159) .. controls (214.62,159) and (167.5,134.26) .. (167.5,103.75) -- cycle ;
%Straight Lines [id:da36505632658461096] 
\draw    (236,53) -- (185.87,33.72) ;
\draw [shift={(184,33)}, rotate = 381.03999999999996] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da357569598162492] 
\draw    (234,52) -- (182.95,63.56) ;
\draw [shift={(181,64)}, rotate = 347.24] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da9574900886541131] 
\draw    (212,149) -- (257.1,164.11) ;
\draw [shift={(259,164.75)}, rotate = 198.53] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

@@

%Shape: Arc [id:dp33725313902395126] 
\draw  [draw opacity=0][line width=0.75]  (219.73,152.25) .. controls (218.31,154.08) and (215.71,155.31) .. (212.73,155.31) .. controls (208.24,155.31) and (204.6,152.51) .. (204.6,149.06) .. controls (204.6,145.61) and (208.24,142.81) .. (212.73,142.81) .. controls (216.16,142.81) and (219.09,144.44) .. (220.29,146.74) -- (212.73,149.06) -- cycle ; \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=0.75]  (219.73,152.25) .. controls (218.31,154.08) and (215.71,155.31) .. (212.73,155.31) .. controls (208.24,155.31) and (204.6,152.51) .. (204.6,149.06) .. controls (204.6,145.61) and (208.24,142.81) .. (212.73,142.81) .. controls (216.16,142.81) and (219.09,144.44) .. (220.29,146.74) ;
%Shape: Arc [id:dp6533092564639917] 
\draw  [draw opacity=0] (216.22,56.17) .. controls (213.28,54.85) and (212,51.09) .. (213.38,47.64) .. controls (213.78,46.63) and (214.38,45.75) .. (215.09,45.04) -- (218.98,49.88) -- cycle ; \draw   (216.22,56.17) .. controls (213.28,54.85) and (212,51.09) .. (213.38,47.64) .. controls (213.78,46.63) and (214.38,45.75) .. (215.09,45.04) ;

% Text Node
\draw (216,26) node [scale=0.7]  {$\gamma _{1} '( s_{2})$};
% Text Node
\draw (164,70) node [scale=0.7]  {$\gamma _{2} '( t_{2})$};
% Text Node
\draw (202,50) node [scale=0.5]  {$\theta $};
% Text Node
\draw (284,143) node [scale=0.7]  {$\gamma _{1} '( s_{1})$};
% Text Node
\draw (286,170) node [scale=0.7]  {$\gamma _{2} '( t_{1})$};
% Text Node
\draw (206.67,136.67) node [scale=0.5]  {$\theta $};
% Text Node
\draw (214,163) node [scale=0.7]  {$p_{1}$};
% Text Node
\draw (237,41) node [scale=0.7]  {$p_{2}$};
% Text Node
\draw (56,93) node   {$E_{1}$};
% Text Node
\draw (390,97) node   {$E_{2}$};

>>>>

%\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
every edge quotes/.append style = {anchor=south, sloped}

%uncomment if require: \path (0,191); %set diagram left start at 0, and has height of 191

%Shape: Ellipse [id:dp10634347053631776] 
\draw   (68.5,97.75) .. controls (68.5,67.24) and (115.62,42.5) .. (173.75,42.5) .. controls (231.88,42.5) and (279,67.24) .. (279,97.75) .. controls (279,128.26) and (231.88,153) .. (173.75,153) .. controls (115.62,153) and (68.5,128.26) .. (68.5,97.75) -- cycle ;
%Shape: Ellipse [id:dp7816950476685691] 
\draw  [color={rgb, 255:red, 163; green, 163; blue, 163 }  ,draw opacity=1 ] (167.5,103.75) .. controls (167.5,73.24) and (214.62,48.5) .. (272.75,48.5) .. controls (330.88,48.5) and (378,73.24) .. (378,103.75) .. controls (378,134.26) and (330.88,159) .. (272.75,159) .. controls (214.62,159) and (167.5,134.26) .. (167.5,103.75) -- cycle ;
%Straight Lines [id:da36505632658461096] 
\draw    (234,52) -- (185.87,33.72) ;
\draw [shift={(184,33)}, rotate = 381.03999999999996] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da357569598162492] 
\draw    (234,52) -- (286.05,39.95) ;
\draw [shift={(288,39.5)}, rotate = 526.97] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da9574900886541131] 
\draw    (212,149) -- (173.91,137.34) ;
\draw [shift={(172,136.75)}, rotate = 377.03] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

@@

% Text Node
\draw (216,26) node [scale=0.7]  {$\gamma _{1} '( s_{2})$};
% Text Node
\draw (312.5,36.5) node [scale=0.7]  {$-\gamma _{2} '( t_{2})$};
% Text Node
\draw (284,143) node [scale=0.7]  {$\gamma _{1} '( s_{1})$};
% Text Node
\draw (147,134) node [scale=0.7]  {$-\gamma _{2} '( t_{1})$};
% Text Node
\draw (214,163) node [scale=0.7]  {$p_{1}$};
% Text Node
\draw (237,41) node [scale=0.7]  {$p_{2}$};
% Text Node
\draw (56,93) node   {$E_{1}$};
% Text Node
\draw (390,97) node   {$E_{2}$};

\coordinate (O) at (212,149) ;
\coordinate (A) at (261.53,140.1) ;
\coordinate (B) at (173.91,137.34) ;

\coordinate (O2) at (234,52);
\coordinate (A2) at (185.87,33.72);
\coordinate (B2) at (286.05,39.95);

\draw (214,130) node [scale=0.7]  {$\theta$};

\draw pic[draw=black, -, angle eccentricity=1.2, angle radius=0.2cm]
{angle=A--O--B};

\draw pic[draw=black, -, angle eccentricity=1.2, angle radius=0.2cm]
{angle=A2--O2--B2};
